\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
small edit
massaging CK intro

\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual All-Loop Integrands}

@@

The kinematic numerators must be $D$-dimensional, Lorentz invariant,
local (polynomial) functions of the graph kinematics with the correct
power counting and external states.  Insisting on a local numerator is
partly a matter of convenience as the ansatz for a rational function
would quickly grow out of control without a guiding principle for what
terms to include.  Locality is also physically motivated since Feynman
rules typically produce polynomial numerators.  While these
assumptions are well motivated from a physical and complexity
standpoint, the literature has featured numerators that violate
locality, modify naive power counting through the inclusion of higher
spin modes, and break manifest Lorentz invariance \cite{Square,
  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
  Cheung:2021zvb}.  These developments suggest that relaxing locality
is a viable alternative when the condition proves too stringent for an
ansatz.  In particular, the most natural way to guarantee locality is
to require the off-shell numerators to be polynomial functions of
kinematics.  However, simply requiring on-shell locality may suffice.
This alternative will be discussed in \cref{nonLocalScattering}.

@@

After using the defining Jacobi relations to relate every graph to the
basis, any remaining Jacobi relations will be referred to as boundary
relations.  In other words, boundary relations (indirectly) relate
basis elements to themselves.  For example, the crossed box numerator
is related to itself via the following Jacobi relation \be % [[19]]
\label{eq:TwoLoopJacobiTwo}
\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
\end{equation}
where the shared propagator is shown in red as before.  Each of the
crossed box numerators can be written in terms of the double box and
penta-triangle so this Jacobi relation places constraints on the basis
numerator \ansatze{}.  While defining Jacobi relations simplify how
many numerators require \ansatze{}, boundary relations place
restrictions on those \ansatze{}.  In principle there could be Jacobi
relations involving tadpoles and BEL graphs, which would be subtle to
handle.  One option is to force the numerators of these graphs to
zero.  However, since these graphs will not contribute to physical
unitarity cuts, we take a different approach.  These graphs are
allowed to have non-zero numerators but any Jacobi relations involving
them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
  Edison:2022jln} for discussions of BELs in the context of
color-kinematics duality.
\paragraph{Color-kinematics duality}
\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH
}
\caption{The 14 non-pathological four-point two-loop cubic diagrams,
  including all dangling tree diagrams.} \label{fig:MaxCuts}
  \end{figure}
\ace{Awkward phrasing/transition.} \nhp{will message language} What has just been described is
sometimes referred to as ``global'' color-kinematics duality because
the Jacobi identities are solved by a single (global) integrand with
off-shell internal lines.  In order to perform the double copy it is
enough to simply satisfy the Jacobi identities on the generalized
unitarity cuts, meaning that each graph can be assigned its own ansatz
\cite{Bern:2015ooa}.  If a global solution cannot be found, this is
one way to enlarge the ansatz where the other option described above
was to incorporate non-local terms in the ``numerators''.  A globally
color-dual integrand is desirable because of its simplicity and
because a color-dual Lagrangian would naively produce precisely this
object.

@@

We can achieve this construction by splitting the gauge group of the
full Yang-Mills action from $G$ to $G_L \times G_R$, where the full
non-abelian gauge symmetry is restored only when we identify
$G_L = G_R$. However, if we break the left gauge group down to
$G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to
$G_R \rightarrow U(N)$, then we are left with a semi-abelian theory
that is gauge invariant in the preferred $U(1)$-directions. We call
this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
\begin{eBox}
\begin{equation}
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\end{equation}
\end{eBox}
where
\begin{equation}
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\end{equation}
\begin{equation}
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
\end{equation}
and $A_\mu$ is in Lorenz gauge.
Here we can think of the abelian vector as a background field that
sources on-shell $A_\mu$ currents. Indeed, as we describe in Appendix
\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
heart of $YZ$-theory \cite{Cheung:2016prv}, J-theory
\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
\cite{Monteiro2011pc}.  Specifically, semi-Abelian YM is simply a
clever reinterpretation of the Lagrangian obtained by integrating an
auxiliary field into the $J$-theory equations of motion.  The Feynman
rule for the cubic vertex is
\begin{equation}
  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
\end{equation}
where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply:
\be
\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
\ee
As one can see, the kinetic term mixes the two gauge fields and has the standard
Feynman rule of $i/k^2$.  We can use the Ward identity of
\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
invariant when the abelian polarizations are taken to be longitudinal,
$\bar{\varepsilon} \rightarrow k$.

@@

\ace{Lets tighten up this paragraph a bit, especially the second half}
It is tempting to try to match the pion four-point two-loop integrand
to ZM on the cuts, but given that the cuts only probe the on-shell
four-point amplitude, which is either subtle or vanishes for ZM, it is
better to compare the off-shell numerators directly.  As local
functions, the numerators never suffer from any of the subtleties of
on-shell 2D kinematics.  Since the physical cuts are difficult to
compare, ZM theory is being used here simply as a tool to eliminate
generalized gauge freedom; ZM theory has the right power counting and
kinematic structure in 2D to compare against.  Since ZM theory is only
being used for the kinematical structure of its numerators, it is
natural to introduce a proportionality constant $z$ between the NLSM
and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
parameter $z$, which would normally be fixed on cuts, effectively
encodes the discrepancy between the coupling constants of the two
theories.\footnote{Floating the proportionality parameter $z$ is also
  motivated because ZM is believed to be quantum mechanically
  different from NLSM even though they are dual classically in two
  dimensions \cite{Nappi:1979ig}.  When the four-point
  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
  $z$ is fixed to $216/565$, which is clearly unrelated to the
  difference in coupling constants.}  This introduces an extra degree of
freedom into the problem.  Mechanically, the pion numerator is matched
to ZM by first taking every possible assignment of right and left
movers for the external particles and then restricting the pion
numerator to 2D.  The loop momenta are restricted to 2D but left
off-shell.  After performing the 2D matching to the following ZM basis numerators:
\be
\ZMBasisDoubleBox =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
\\
\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
\be
\ZMBasisPentaTriangle =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
\\
\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
there are only 365 parameters of generalized gauge freedom. An overview of ZM theory and its color-dual construction can be found at the end of \cref{sec:CKLagrangians}.

The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerator is forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerator appearing in the
ancillary files makes exactly this choice.

@@

Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. The component definition of our spinor bracket that are consistent with the conventions above,
\begin{align}
\langle ab \rangle &= \frac{(a_1 + i a_2)(b_0+b_3)-(b_1 + i b_2)(a_0+a_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\\
[ab] &= \frac{(b_1 - i b_2)(a_0+a_3)-(a_1 - i a_2)(b_0+b_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\end{align}
where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$, one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
\begin{equation}
s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,.
\end{equation}
Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
\begin{equation}\label{eq:4DPols}
\begin{aligned}
k_a \cdot \varepsilon_b^{(+)} &= \frac{\langle q a \rangle[ab]}{\sqrt{2}\langle q b\rangle}\,,
\qquad\quad \qquad
k_a \cdot \varepsilon_b^{(-)} = -\frac{[qa]\langle ab\rangle}{\sqrt{2}[qb]}\,,
\\
\varepsilon_a^{(-)}\cdot \varepsilon_b^{(+)} &= - \frac{\langle q a\rangle [qb]}{ [qa]\langle q b\rangle} \,,
\qquad \qquad
\varepsilon_a^{(\pm)}\cdot \varepsilon_b^{(\pm)} = 0 \,,
\end{aligned}
\end{equation}
Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets. In terms of light-cone coordinates that we employed above in \cref{sec:CKLagrangians}, the angles and squares can be rewritten as follows:
\begin{align}
\langle ab \rangle &= \frac{a_w b_u-a_u b_w}{\sqrt{a_ub_u}}\,,
\\
[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,,
\end{align}
The conventions we use in the text where the holomorphic spinor, $X(p,k)$, carries extra mass dimension essentially amounts to shifting the bracket by the following overall factor:
\begin{align}
\langle ab \rangle &\rightarrow a_w b_u-a_u b_w \equiv X(a,b)\,,
\\
[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\,,
\end{align}
With this, we still obtain the same completeness relation for the SDYM spinors:
\begin{equation}
X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
\end{equation}
\section{Regulating BEL integrals}\label{BELreg}
At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles. Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.  Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
\begin{equation}
N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
\end{equation}
where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops. Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
\begin{equation}
N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
\end{equation}
and similarly so for the internal vector contribution:
\begin{equation}
 (F^1F^2\cdots F^n) = D (l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
\end{equation}
The dimension dependent factor essentially counts that number of internal vector states. While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM. However, the scalar contribution, that comes dressed with an overall factor $D$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality. We leave this as a direction of future work.

>>>>

\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual Multi-Loop Integrands}

@@

The kinematic numerators must be $D$-dimensional, Lorentz invariant,
local (polynomial) functions of the graph kinematics with the correct
power counting and external states. Locality is also physically motivated since Feynman
rules by construction produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
kinematics. However, insisting on a local numerator is
partly a matter of convenience as the ansatz for a rational function
would quickly grow out of control without a guiding principle for what
terms to include.  While these
assumptions are well motivated from a physical and complexity
standpoint, the literature has featured numerators that violate
locality, modify naive power counting through the inclusion of higher
spin modes, and break manifest Lorentz invariance \cite{Square,
  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
  Cheung:2021zvb}.  These developments suggest that relaxing locality
is a viable alternative when the condition proves too stringent for an
ansatz. As such, requiring instead that locality is only realized \textit{on-shell} may suffice.
This alternative will be discussed in \cref{nonLocalScattering}.

\paragraph{Color-kinematics duality}

@@

After using the defining Jacobi relations to relate every graph to the
basis, any remaining Jacobi relations will be referred to as boundary
relations.  In other words, boundary relations (indirectly) relate
basis elements to themselves.  For example, the crossed box numerator
is related to itself via the following Jacobi relation \be % [[19]]
\label{eq:TwoLoopJacobiTwo}
\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
\end{equation}
where the shared propagator is shown in red as before.  Each of the
crossed box numerators can be written in terms of the double box and
penta-triangle so this Jacobi relation places constraints on the basis
numerator \ansatze{}.  While defining Jacobi relations simplify how
many numerators require \ansatze{}, boundary relations place
restrictions on those \ansatze{}.  In principle there could be Jacobi
relations involving tadpoles and BEL graphs, which would be subtle to
handle.  One option is to force the numerators of these graphs to
zero.  However, since these graphs will not contribute to physical
unitarity cuts, we take a different approach.  These graphs are
allowed to have non-zero numerators but any Jacobi relations involving
them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
  Edison:2022jln} and \cref{BELref} for discussions of BELs in the context of
color-kinematics duality.

\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH
}
\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
  \end{figure}
What we have just been described is
sometimes referred to as ``global'' color-kinematics duality because
the Jacobi identities are solved by a single (global) integrand with
off-shell internal lines.  In order to perform the double copy it is
enough to simply satisfy the Jacobi identities on the generalized
unitarity cuts, meaning that each graph can be assigned its own ansatz
\cite{Bern:2015ooa}.  If a global solution cannot be found, this is
one way to enlarge the ansatz where the other option described above
was to incorporate non-local terms in the ``numerators''.  A globally
color-dual integrand is desirable because of its simplicity and
because a color-dual Lagrangian would naively produce precisely this
object.

@@

We can achieve this construction by splitting the gauge group of the
full Yang-Mills action from $G$ to $G_L \times G_R$, where the full
non-abelian gauge symmetry is restored only when we identify
$G_L = G_R$. However, if we break the left gauge group down to
$G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to
$G_R \rightarrow U(N)$, then we are left with a semi-abelian theory
that is gauge invariant in the preferred $U(1)$-directions. We call
this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
\begin{eBox}
\begin{equation}
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\end{equation}
\end{eBox}
where
\begin{equation}
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\end{equation}
\begin{equation}
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
\end{equation}
and $A_\mu$ is in Lorenz gauge.
Here we can think of the abelian vector as a background field that
sources on-shell $A_\mu$ currents. Indeed, as we describe in Appendix
\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
\cite{Monteiro2011pc}.  Specifically, semi-Abelian YM is simply a
clever reinterpretation of the Lagrangian obtained by integrating an
auxiliary field into the $J$-theory equations of motion.  The Feynman
rule for the cubic vertex is
\begin{equation}
  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
\end{equation}
where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply:
\be
\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
\ee
As one can see, the kinetic term mixes the two gauge fields and has the standard
Feynman rule of $i/k^2$.  We can use the Ward identity of
\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
invariant when the abelian polarizations are taken to be longitudinal,
$\bar{\varepsilon} \rightarrow k$.

@@

\ace{Lets tighten up this paragraph a bit, especially the second half}
It is tempting to try to match the pion four-point two-loop integrand
to ZM on the cuts, but given that the cuts only probe the on-shell
four-point amplitude, which is either subtle or vanishes for ZM, it is
better to compare the off-shell numerators directly.  As local
functions, the numerators never suffer from any of the subtleties of
on-shell 2D kinematics.  Since the physical cuts are difficult to
compare, ZM theory is being used here simply as a tool to eliminate
generalized gauge freedom; ZM theory has the right power counting and
kinematic structure in 2D to compare against.  Since ZM theory is only
being used for the kinematical structure of its numerators, it is
natural to introduce a proportionality constant $z$ between the NLSM
and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
parameter $z$, which would normally be fixed on cuts, effectively
encodes the discrepancy between the coupling constants of the two
theories.\footnote{Floating the proportionality parameter $z$ is also
  motivated because ZM is believed to be quantum mechanically
  different from NLSM even though they are dual classically in two
  dimensions \cite{Nappi:1979ig}.  When the four-point
  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
  $z$ is fixed to $216/565$, which is clearly unrelated to the
  difference in coupling constants.}  This introduces an extra degree of
freedom into the problem.  Mechanically, the pion numerator is matched
to ZM by first taking every possible assignment of right and left
movers for the external particles and then restricting the pion
numerator to 2D.  The loop momenta are restricted to 2D but left
off-shell.  After performing the 2D matching to the following ZM basis numerators:
\be
\ZMBasisDoubleBox =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
\\
\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
\be
\ZMBasisPentaTriangle =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
\\
\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
there are only 365 parameters of generalized gauge freedom. An overview of ZM theory and its color-dual construction can be found at the end of \cref{sec:CKLagrangians}. The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerator is forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerator appearing in the
ancillary files makes exactly this choice.

@@

Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. The component definition of our spinor bracket that are consistent with the conventions above,
\begin{align}
\langle ab \rangle &= \frac{(a_1 + i a_2)(b_0+b_3)-(b_1 + i b_2)(a_0+a_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\\
[ab] &= \frac{(b_1 - i b_2)(a_0+a_3)-(a_1 - i a_2)(b_0+b_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\end{align}
where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$, one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
\begin{equation}
s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,.
\end{equation}
Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
\begin{equation}\label{eq:4DPols}
\begin{aligned}
k_a \cdot \varepsilon_b^{(+)} &= \frac{\langle q a \rangle[ab]}{\sqrt{2}\langle q b\rangle}\,,
\qquad\quad \qquad
k_a \cdot \varepsilon_b^{(-)} = -\frac{[qa]\langle ab\rangle}{\sqrt{2}[qb]}\,,
\\
\varepsilon_a^{(-)}\cdot \varepsilon_b^{(+)} &= - \frac{\langle q a\rangle [qb]}{ [qa]\langle q b\rangle} \,,
\qquad \qquad
\varepsilon_a^{(\pm)}\cdot \varepsilon_b^{(\pm)} = 0 \,,
\end{aligned}
\end{equation}
Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets. In terms of light-cone coordinates that we employed above in \cref{sec:CKLagrangians}, the angles and squares can be rewritten as follows:
\begin{align}
\langle ab \rangle &= \frac{a_w b_u-a_u b_w}{\sqrt{a_ub_u}}\,,
\\
[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,,
\end{align}
The conventions we use in the text where the holomorphic spinor, $X(p,k)$, carries extra mass dimension essentially amounts to shifting the bracket by the following overall factor:
\begin{align}
\langle ab \rangle &\rightarrow a_w b_u-a_u b_w \equiv X(a,b)\,,
\\
[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\,,
\end{align}
With this, we still obtain the same completeness relation for the SDYM spinors:
\begin{equation}
X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
\end{equation}
\section{Regulating BEL integrals}\label{BELreg}
At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles. Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.  Thus, $YZ$ theory gives us the following one-loop $n$-gon numerator:
\begin{equation}
N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+ (F^1F^2\cdots F^n)
\end{equation}
where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops. Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
\begin{equation}
N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
\end{equation}
and similarly so for the internal vector contribution:
\begin{equation}
 (F^1F^2\cdots F^n) = D (l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
\end{equation}
The dimension dependent factor essentially counts that number of internal vector states. While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM. However, the scalar contribution, that comes dressed with an overall factor $D$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality. We leave this as a direction of future work.
